---
title: "Coursera Data Products Course Assignment"
subtitle: "Week 3 - Assignment 2 Submission - Plotly"
date: "June 10, 2018"
output: 
    ioslides_presentation:
      widescreen: true
      smaller: true
---

```{r,echo=FALSE}
library(plotly)
```
## Purpose

- The purpose of this assignment is to illustrate how R markdown can deliver output in presentation form.
- It also illustrates how easy it is to integrate a plotly object into the presentation.
- For this example, the swiss dataset has been selected.


## Plotly analysis

- In this slide we with inspect the swiss data set and try to establish how the population fertility is dependant on various social factors.
- 4 dimensions are represented on this plot. fertility, Education, % Population Engaged in Agriculture & % Catholic

```{r,warning=FALSE,message=FALSE,echo=FALSE}
p <- plot_ly(swiss, x = ~Education, y = ~Fertility,
             text = ~paste("%Education: ", Education, '<br>Fertility:', Fertility,'<br>% Agrarian:',Agriculture,'<br>% Catholic',Catholic),
  marker = list(size = ~Agriculture/2,
                       # color = 'rgba(150, 0, 150, .9)',
                      color = ~Catholic,
                       line = list(color = 'rgba(75, 0,75, .8)',
                                   width = 2))) %>% 
  layout(title = 'Fertility by province dependent on Education, <br>%Agrarian population (size) & % Catholic (color)',
         yaxis = list(zeroline = FALSE),
         xaxis = list(zeroline = FALSE))


htmltools::tagList(list(p, p))
```

## Thank you